### 2021-02-15 crowd-forecast/email-templates/email-template.Rmd

```{r echo=FALSE}

@@

```{r plot-forecasts, echo=FALSE, out.width="49%", fig.show="hold", fig.cap = "Plot of the forecasts"}

forecast_date <- covid.german.forecasts::latest_weekday(Sys.Date())

filter_truth <- list('target_end_date >= Sys.Date() - 14 * 7')
models <- c("anonymous_Human", "EpiExpert-ensemble")
filter_forecasts <- list("model %in% 'EpiExpert-ensemble'", 
                         paste0("forecast_date == '", forecast_date, "'"))

@@

forecast_date <- covid.german.forecasts::latest_weekday(Sys.Date())

@@

```{r rank-over-time, echo=FALSE, fig.align = "center", fig.width=10, fig.height=8, out.width="80%", fig.cap = "Ranking over time"}
scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = c("model", 
                                                          "location_name", 
                                                          "target_type",
                                                          "forecast_date"), 
                                       compute_relative_skill = FALSE)

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r plot-forecasts, echo=FALSE, out.width="49%", fig.show="hold"}

if (weekdays(Sys.Date()) == "Monday") {
  forecast_date <- covid.german.forecasts::latest_weekday(Sys.Date() - 7)
} else {
  forecast_date <- covid.german.forecasts::latest_weekday(Sys.Date())
}

filter_truth <- list('target_end_date >= Sys.Date() - 14 * 7')
filter_forecasts <- list("model %in% 'EpiExpert-ensemble'", 
                         paste0("forecast_date == '", forecast_date, "'"))

@@

@@

```{r rank-over-time, echo=FALSE, fig.align = "center", fig.width=10, fig.height=8, out.width="80%"}
scores <- scoringutils::eval_forecasts(data,
                                         summarise_by = c("model", 
                                                          "location_name", 
                                                          "target_type",
                                                          "forecast_date"), 
                                       compute_relative_skill = FALSE)
